---
title: "Conversion for R Markdown and Quarto"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Conversion for R Markdown and Quarto}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

## User goal

This vignette helps instructors decide whether to target `learnr` or `quarto-live` when converting existing R Markdown or Quarto material.

## Minimal examples

```{r eval=FALSE}
library(tutorizeR)

tutorize("lesson.Rmd", format = "learnr", assessment = "both")
tutorize("lesson.qmd", format = "quarto-live", assessment = "code")
```

## Choosing an output format

Use `learnr` when the course already supports RStudio or Shiny-based tutorials and when `gradethis` feedback is useful. Use `quarto-live` when browser-based execution is preferred and the teaching project has the Quarto live extension installed.

## Realistic installed example

```{r eval=FALSE}
library(tutorizeR)

example_dir <- system.file("examples", "example_course_module", package = "tutorizeR")
work_dir <- file.path(tempdir(), "tutorizeR-formats")
dir.create(work_dir, recursive = TRUE, showWarnings = FALSE)
file.copy(file.path(example_dir, "lesson-source.qmd"), work_dir, overwrite = TRUE)
file.copy(file.path(example_dir, "student_activity.csv"), work_dir, overwrite = TRUE)

qb <- load_question_bank(file.path(example_dir, "question-bank"))

learnr_report <- tutorize(
  input = file.path(work_dir, "lesson-source.qmd"),
  output_dir = work_dir,
  format = "learnr",
  assessment = "both",
  question_bank = qb,
  overwrite = TRUE,
  verbose = FALSE
)

live_report <- tutorize(
  input = file.path(work_dir, "lesson-source.qmd"),
  output_dir = work_dir,
  format = "quarto-live",
  assessment = "both",
  question_bank = qb,
  overwrite = TRUE,
  verbose = FALSE
)
```

## Limits

When targeting `quarto-live`, install the extension in the teaching project:

```{r eval=FALSE}
system("quarto add r-wasm/quarto-live")
```

Generated output should be reviewed in the environment where students will use it, because package availability and browser execution settings can differ.

## Reproducibility checklist

```{r eval=FALSE}
file.exists(learnr_report$output_file)
file.exists(live_report$output_file)
```
