---
title: "Documentation Website"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Documentation Website}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

## Purpose

The repository includes a pkgdown configuration so that the README, function reference pages, and vignettes can be rendered as a documentation website. The site configuration is stored in `_pkgdown.yml`.

The generated site is written to `pkgdown/`. This keeps generated website files separate from the repository's source documentation in `docs/`.

## Build Locally

```{r eval=FALSE}
library(pkgdown)

build_site()
```

For a documentation-only check, build the articles and reference index locally before pushing changes.

```{r eval=FALSE}
library(pkgdown)

build_articles()
build_reference()
```

## Article Groups

The pkgdown site organizes vignettes into four groups:

- Start here: first conversion workflow and common teaching scenarios.
- Authoring and assessment: tags, MCQs, question banks, and output formats.
- Course operations: batch conversion, linting, debugging, and educational use cases.
- Project documentation: site maintenance and reviewer-facing readiness notes.

## Maintenance Checklist

Before publishing documentation changes, run:

```bash
Rscript -e "devtools::document()"
Rscript -e "testthat::test_local('.')"
Rscript -e "lintr::lint_package()"
Rscript -e "pkgdown::build_site()"
```

If a user-facing function, argument, or workflow changes, update at least one vignette and the relevant reference documentation.
