---
title: "Getting started for teachers"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started for teachers}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

`tutorizeR` converts existing `.Rmd` or `.qmd` files into interactive
teaching material.

## Minimal reproducible workflow

```{r eval=FALSE}
library(tutorizeR)

# Convert one file to learnr
report <- tutorize(
  input = "lesson.qmd",
  format = "learnr",
  assessment = "both",
  overwrite = TRUE
)

print(report)
```

## Batch conversion

```{r eval=FALSE}
folder_report <- convert_folder(
  dir = "course_material/",
  recursive = TRUE,
  format = "learnr",
  assessment = "both",
  overwrite = TRUE
)

print(folder_report)
```

## Source annotation tags

Use comments inside R chunks:

- `# tutorizeR: skip`
- `# tutorizeR: exercise-only`
- `# tutorizeR: solution-only`
- `# tutorizeR: mcq`
- `# tutorizeR: narrative-only`
- `# tutorizeR: locked`
- `# tutorizeR: hints=Hint 1|Hint 2`

## Explicit MCQ block schema

```text
```{tutorizeR-mcq}
question: "2 + 2 = ?"
answers:
  - text: "4"
    correct: true
  - text: "5"
    correct: false
```
```
