---
title: "Getting Started with tutorizeR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with tutorizeR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

`tutorizeR` converts existing `.Rmd` or `.qmd` files into interactive teaching material. The usual workflow is to keep the instructor's source document as the single source of truth, then generate a student-facing tutorial for a specific teaching context.

## Minimal workflow

```{r eval=FALSE}
library(tutorizeR)

report <- tutorize(
  input = "lesson.qmd",
  format = "learnr",
  assessment = "both",
  overwrite = TRUE
)

print(report)
```

The returned report records the input file, output file, format, assessment mode, generated exercises, MCQs, warnings, lint results, and render status.

## Batch conversion

```{r eval=FALSE}
library(tutorizeR)

folder_report <- convert_folder(
  dir = "course_material/",
  recursive = TRUE,
  format = "learnr",
  assessment = "both",
  overwrite = TRUE
)

print(folder_report)
```

## Pre-conversion linting

```{r eval=FALSE}
library(tutorizeR)

lint <- lint_source("lesson.qmd", strict = FALSE)
print(lint)
```

## Source annotation tags

Use comments inside R chunks:

- `# tutorizeR: skip`
- `# tutorizeR: exercise-only`
- `# tutorizeR: solution-only`
- `# tutorizeR: mcq`
- `# tutorizeR: narrative-only`
- `# tutorizeR: locked`
- `# tutorizeR: hints=Hint 1|Hint 2`

## Explicit MCQ block schema

The YAML content inside a `tutorizeR-mcq` block has this structure:

```yaml
question: "2 + 2 = ?"
answers:
  - text: "4"
    correct: true
  - text: "5"
    correct: false
```

## Reviewer smoke test

The package includes a complete example module in `inst/examples/example_course_module/`. After installation, an instructor can locate it with:

```{r eval=FALSE}
system.file("examples", "example_course_module", package = "tutorizeR")
```
