---
title: "JOSE Submission Readiness"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{JOSE Submission Readiness}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

This vignette points reviewers to the repository artifacts prepared for a future Journal of Open Source Education submission.

## Main artifacts

- `paper/paper.md`
- `paper/paper.bib`
- `docs/jose_blockers_report.md`
- `docs/educational_use_evidence.md`
- `docs/jose_review_checklist.md`
- `docs/jose_submission_guide.md`
- `inst/examples/example_course_module/`

## Local verification

```{r eval=FALSE}
testthat::test_local()
lintr::lint_package()

tmpdir <- tempfile("tutorizeR-source-")
dir.create(tmpdir)
system2("rsync", c(
  "-a",
  "--exclude=.git",
  "--exclude=*.Rcheck",
  "--exclude=*.tar.gz",
  "./",
  file.path(tmpdir, "tutorizeR/")
))
old <- setwd(file.path(tmpdir, "tutorizeR"))
on.exit(setwd(old), add = TRUE)
system("R CMD build .")
system("R CMD check --as-cran --no-manual tutorizeR_0.4.4.tar.gz")
```

## Evidence boundaries

Educational use cases are documented in the repository.

- Actual classroom deployment: Not verifiable from repository contents.
- Broad external adoption: Not verifiable from repository contents.
- Public GitHub history: Not verifiable from repository contents.
