---
title: "JOSE Submission Readiness"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{JOSE Submission Readiness}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

This vignette points reviewers to the repository artifacts prepared for a future Journal of Open Source Education submission.

## Main artifacts

- `paper/paper.md`
- `paper/paper.bib`
- `docs/jose_audit.md`
- `docs/educational_use_cases.md`
- `docs/jose_checklist.md`
- `docs/jose_submission_report.md`
- `inst/examples/example_course_module/`

## Local verification

```{r eval=FALSE}
testthat::test_local()
lintr::lint_package()

system("R CMD build .")
system("R CMD check --as-cran --no-manual tutorizeR_*.tar.gz")
```

## Evidence boundaries

Educational use cases are documented in the repository. Actual classroom adoption, external adoption, and public GitHub history are not verifiable from local repository contents.

