---
title: "Using tutorizeR in Large Undergraduate Courses"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using tutorizeR in Large Undergraduate Courses}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

Large undergraduate courses need consistent materials, reproducible updates, and clear handoffs between instructors and teaching assistants. `tutorizeR` is designed for this kind of operational teaching workflow.

Specific deployment in named courses such as STT-1100 or STT-4230 is not verifiable from repository contents.

## Course folder workflow

```text
course/
  lessons/
    week01-introduction.qmd
    week02-data-import.qmd
    week03-visualization.qmd
  question-bank/
    core-concepts.yml
  tutorials/
  reports/
```

## Batch conversion

```{r eval=FALSE}
library(tutorizeR)

qb <- load_question_bank("course/question-bank")

folder_report <- convert_folder(
  dir = "course/lessons",
  recursive = TRUE,
  output_dir = "course/tutorials",
  format = "learnr",
  assessment = "both",
  question_bank = qb,
  mcq_source = "mixed",
  lint_strict = TRUE,
  overwrite = TRUE
)

print(folder_report)
```

## Teaching assistant review

Teaching assistants can review generated outputs and reports before release:

```{r eval=FALSE}
library(tutorizeR)

lint <- lint_source(
  input = "course/lessons/week03-visualization.qmd",
  question_bank = qb,
  strict = FALSE
)

print(lint)
```

## Operational benefits

The main benefit is not that tutorials are generated automatically once. The benefit is that a whole course team can regenerate the same materials after corrections, new datasets, or revised learning objectives.

