---
title: "Converting a Quarto Lesson into an Interactive Tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Converting a Quarto Lesson into an Interactive Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

Many instructors prepare lessons in Quarto because it supports narrative, executable code, figures, tables, and reproducible publishing. `tutorizeR` keeps that authoring workflow intact while producing an interactive tutorial for students.

## Source lesson

A source `.qmd` lesson can contain narrative text, setup code, examples, and MCQ blocks:

    ---
    title: "Weekly study patterns"
    ---

    ## Learning goal

    Students will summarize study time and relate it to quiz performance.

    ```r
    library(tidyverse)
    activity <- readr::read_csv("student_activity.csv")
    ```

    ```r
    activity |>
      group_by(program) |>
      summarise(mean_hours = mean(study_hours), .groups = "drop")
    ```

    ```yaml
    question: "Which summary is most appropriate for comparing programs?"
    answers:
      - text: "Mean study hours by program"
        correct: true
      - text: "The first row of the data"
        correct: false
    ```

## Conversion

```{r eval=FALSE}
library(tutorizeR)

report <- tutorize(
  input = "lesson-source.qmd",
  output_dir = "generated",
  format = "learnr",
  assessment = "both",
  overwrite = TRUE
)

print(report)
```

## Quarto live output

For browser-executable Quarto output, target `quarto-live`:

```{r eval=FALSE}
library(tutorizeR)

report <- tutorize(
  input = "lesson-source.qmd",
  output_dir = "generated",
  format = "quarto-live",
  assessment = "code",
  overwrite = TRUE
)

print(report)
```

The `quarto-live` workflow requires the Quarto live extension in the teaching project. That dependency is intentionally not vendored by `tutorizeR`.
