---
title: Introduction to Data Visualization and Summarisation with R
author: Example instructor
output: learnr::tutorial
runtime: shiny_prerendered
---


## Learning objectives

By the end of this lesson, students should be able to:

- import a small CSV file;
- compute grouped summaries with `dplyr`;
- create a scatterplot with `ggplot2`;
- interpret an exploratory pattern without overclaiming.

## Context

The synthetic dataset records weekly study activity for a small group of students. The lesson is intentionally compact so that instructors can inspect the complete conversion workflow.

## Setup

```{r setup, include=FALSE}
library(dplyr)
library(ggplot2)
library(readr)

activity <- read_csv("student_activity.csv", show_col_types = FALSE)
library(learnr)
library(gradethis)
gradethis_setup()
```


## Instructor demonstration

_Locked exercise: enable this block only for demonstration._
```{r trz-ex-demo-preview, exercise.lines=3, exercise=TRUE}
# Write your code below
```

```{r trz-sol-demo-preview, include=FALSE}
head(activity, 3)
```

```{r trz-mcq-demo-preview, echo=FALSE}
learnr::question(
  "In ggplot2, which aesthetic should be mapped to show quiz score on the vertical axis?",
  learnr::answer("y", correct = TRUE),
  learnr::answer("x", correct = FALSE),
  learnr::answer("color", correct = FALSE),
  allow_retry = TRUE
)
```


## Data manipulation exercise

**Hint(s)**
- Group by program before summarising
- Compute mean study hours and mean quiz score
- Use .groups = "drop"

```{r trz-ex-summarize-program, exercise.lines=7, exercise=TRUE}
# Write your code below
```

```{r trz-sol-summarize-program, include=FALSE}
activity |>
  group_by(program) |>
  summarise(
    mean_hours = mean(study_hours),
    mean_score = mean(quiz_score),
    .groups = "drop"
  )
```

```{r trz-mcq-summarize-program, echo=FALSE}
learnr::question(
  "What does the code in chunk 'summarize-program' do?",
  learnr::answer("Answer A (edit me)", correct = TRUE),
  learnr::answer("Answer B (edit me)", correct = FALSE),
  learnr::answer("Answer C (edit me)", correct = FALSE),
  allow_retry = TRUE
)
```


```{r trz-mcq-explicit-004, echo=FALSE}
learnr::question(
  "Which variable identifies the academic program?",
  learnr::answer("program", correct = TRUE),
  learnr::answer("week", correct = FALSE),
  learnr::answer("quiz_score", correct = FALSE),
  allow_retry = TRUE
)
```


```{r trz-mcq-bank-005-001, echo=FALSE}
learnr::question(
  "In ggplot2, which aesthetic should be mapped to show quiz score on the vertical axis?",
  learnr::answer("y", correct = TRUE),
  learnr::answer("x", correct = FALSE),
  learnr::answer("color", correct = FALSE),
  allow_retry = TRUE
)
```


## Visualization exercise

**Hint(s)**
- Map study_hours to x and quiz_score to y
- Use color for program
- Use geom_point()

```{r trz-ex-plot-study-score, exercise.lines=7, exercise=TRUE}
# Write your code below
```

```{r trz-sol-plot-study-score, include=FALSE}
ggplot(activity, aes(x = study_hours, y = quiz_score, color = program)) +
  geom_point(size = 2) +
  labs(
    x = "Study hours",
    y = "Quiz score",
    color = "Program"
  )
```

```{r trz-mcq-plot-study-score, echo=FALSE}
learnr::question(
  "What does the code in chunk 'plot-study-score' do?",
  learnr::answer("Answer A (edit me)", correct = TRUE),
  learnr::answer("Answer B (edit me)", correct = FALSE),
  learnr::answer("Answer C (edit me)", correct = FALSE),
  allow_retry = TRUE
)
```


## Instructor solution note

```{r trz-sol-interpretation-note, include=FALSE}
"In this small synthetic dataset, higher study time is associated with higher quiz score. This is not causal evidence."
```


## Manual interpretation

Students should describe the plot cautiously. The dataset is small and synthetic, so the goal is to practice code and interpretation rather than estimate a population effect.
