---
title: "Introduction to Data Visualization and Summarisation with R"
author: "Example instructor"
format: html
---

## Learning objectives

By the end of this lesson, students should be able to:

- import a small CSV file;
- compute grouped summaries with `dplyr`;
- create a scatterplot with `ggplot2`;
- interpret an exploratory pattern without overclaiming.

## Context

The synthetic dataset records weekly study activity for a small group of students. The lesson is intentionally compact so that instructors can inspect the complete conversion workflow.

## Setup

```{r setup}
library(dplyr)
library(ggplot2)
library(readr)

activity <- read_csv("student_activity.csv", show_col_types = FALSE)
```

## Instructor demonstration

```{r demo-preview}
# tutorizeR: locked
head(activity, 3)
```

## Data manipulation exercise

```{r summarize-program}
# tutorizeR: hints=Group by program before summarising|Compute mean study hours and mean quiz score|Use .groups = "drop"
activity |>
  group_by(program) |>
  summarise(
    mean_hours = mean(study_hours),
    mean_score = mean(quiz_score),
    .groups = "drop"
  )
```

```{tutorizeR-mcq}
question: "Which variable identifies the academic program?"
answers:
  - text: "program"
    correct: true
  - text: "week"
    correct: false
  - text: "quiz_score"
    correct: false
allow_retry: true
```

```{tutorizeR-mcq-ref}
ids: [visualization-aesthetic]
strategy: ordered
shuffle_answers: false
```

## Visualization exercise

```{r plot-study-score}
# tutorizeR: hints=Map study_hours to x and quiz_score to y|Use color for program|Use geom_point()
ggplot(activity, aes(x = study_hours, y = quiz_score, color = program)) +
  geom_point(size = 2) +
  labs(
    x = "Study hours",
    y = "Quiz score",
    color = "Program"
  )
```

## Instructor solution note

```{r interpretation-note}
# tutorizeR: solution-only
"In this small synthetic dataset, higher study time is associated with higher quiz score. This is not causal evidence."
```

## Manual interpretation

Students should describe the plot cautiously. The dataset is small and synthetic, so the goal is to practice code and interpretation rather than estimate a population effect.

