---
title: "Study Patterns and Quiz Performance"
author: "Example instructor"
format: html
---

## Learning objectives

By the end of this lesson, students should be able to:

- import a local CSV file;
- compute grouped summaries with `dplyr`;
- visualize a relationship with `ggplot2`;
- interpret a simple data summary in context.

## Setup

```{r setup}
library(tidyverse)

activity <- readr::read_csv("student_activity.csv")
```

## Inspect the data

```{r inspect-data}
glimpse(activity)
```

## Summarise by program

```{r summarize-program}
# tutorizeR: hints=Group by program before summarising|Use .groups = "drop"
activity |>
  group_by(program) |>
  summarise(
    mean_hours = mean(study_hours),
    mean_score = mean(quiz_score),
    .groups = "drop"
  )
```

```{tutorizeR-mcq}
question: "Which variable identifies the academic program?"
answers:
  - text: "program"
    correct: true
  - text: "week"
    correct: false
  - text: "quiz_score"
    correct: false
allow_retry: true
```

## Visualize study time and quiz score

```{r plot-study-score}
# tutorizeR: hints=Map study_hours to x and quiz_score to y|Use color for program
ggplot(activity, aes(x = study_hours, y = quiz_score, color = program)) +
  geom_point(size = 2) +
  geom_smooth(method = "lm", se = FALSE) +
  labs(
    x = "Study hours",
    y = "Quiz score",
    color = "Program"
  )
```

## Interpretation

The example is intentionally small. Its purpose is to practice a reproducible workflow rather than estimate a stable population relationship.

