---
title: Study Patterns and Quiz Performance
author: Example instructor
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(tidyverse)
library(learnr)
library(gradethis)
gradethis_setup()

activity <- readr::read_csv("student_activity.csv")
```

## Learning objectives

By the end of this lesson, students should be able to:

- import a local CSV file;
- compute grouped summaries with `dplyr`;
- visualize a relationship with `ggplot2`;
- interpret a simple data summary in context.

## Inspect the data

```{r trz-ex-inspect-data, exercise.lines=3, exercise=TRUE}
# Write your code here
```

```{r trz-sol-inspect-data, include=FALSE}
glimpse(activity)
```

## Summarise by program

Hint:
- Group by program before summarising
- Use .groups = "drop"

```{r trz-ex-summarize-program, exercise.lines=7, exercise=TRUE}
# Write your code here
```

```{r trz-sol-summarize-program, include=FALSE}
activity |>
  group_by(program) |>
  summarise(
    mean_hours = mean(study_hours),
    mean_score = mean(quiz_score),
    .groups = "drop"
  )
```

```{r trz-mcq-explicit-004, echo=FALSE}
learnr::question(
  "Which variable identifies the academic program?",
  learnr::answer("program", correct = TRUE),
  learnr::answer("week", correct = FALSE),
  learnr::answer("quiz_score", correct = FALSE),
  allow_retry = TRUE
)
```

## Visualize study time and quiz score

Hint:
- Map study_hours to x and quiz_score to y
- Use color for program

```{r trz-ex-plot-study-score, exercise.lines=9, exercise=TRUE}
# Write your code here
```

```{r trz-sol-plot-study-score, include=FALSE}
ggplot(activity, aes(x = study_hours, y = quiz_score, color = program)) +
  geom_point(size = 2) +
  geom_smooth(method = "lm", se = FALSE) +
  labs(
    x = "Study hours",
    y = "Quiz score",
    color = "Program"
  )
```

## Interpretation

The example is intentionally small. Its purpose is to practice a reproducible workflow rather than estimate a stable population relationship.

